Sample size

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:bug: - output full summary of simulations
:art: - add plot code for sample size simulations

run_simulations <- function(n, sd) {
  data <- simulate_data(n, sd)
  brm_model <- run_brm(data)

  sd_team <- as_tibble(summary(brm_model)$team)

@@

```{r run-sims}
sample_sims <- tibble(
  n_teams = n_ts_qs$n_teams,
  quants = n_ts_qs$quantiles,
  sd_team = map2(
    n_teams, quants,
    ~run_simulations(.x, .y)
  )
)

saveRDS(sample_sims, "./models/sims/sample_sims.rds")
```

```{r plot, eval=FALSE, include=FALSE}
sd_20 <- tibble(
  team_sd = quantiles,
  sd = sds_20,
  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 20
)

sd_25 <- tibble(
  team_sd = quantiles,
  sd = sds_25,
  min = sapply(sds_25, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_25, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 25
)

sd_30 <- tibble(
  team_sd = quantiles,
  sd = sds_30,
  min = sapply(sds_30, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_30, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 30
)

sd_35 <- tibble(
  team_sd = quantiles,
  sd = sds_35,
  min = sapply(sds_35, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_35, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 35
)

sd_40 <- tibble(
  team_sd = quantiles,
  sd = sds_40,
  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 40
)

bind_rows(sd_20, sd_25,sd_30, sd_35, sd_40) %>%
  ggplot(aes(team_sd, width, colour = as.factor(n))) +
  geom_line() +
  geom_point(size = 4) +
  geom_hline(yintercept = 1) +
  annotate("text", 0.9, 1.3, label = "1 SD") +
  geom_hline(yintercept = 2, linetype = "dashed") +
  annotate("text", 0.9, 2.3, label = "2 SD") +
  geom_hline(yintercept = 3, linetype = "dotted") +
  annotate("text", 0.9, 3.3, label = "3 SD") +
  ylim(0, 8) +
  scale_color_brewer() +
  labs(
    title = "95% CrI width depending on teams' true SD and number of teams",
    x = "Teams' true standard deviation",
    y = "95% CrI width (standard units)",
    colour = "N of teams"
  )

>>>>

run_simulations <- function(n, sd) {
  data <- simulate_data(n, sd)

  cat("Model:", n, sd, "\n")
  brm_model <- run_brm(data)

  sd_team <- summary(brm_model)

@@

```{r run-sims}
sample_file <- "./models/sims/sample_sims.rds"

if (file.exists(sample_file)) {
  sample_sims <- readRDS(sample_file)
} else {
  sample_sims <- tibble(
    n_teams = n_ts_qs$n_teams,
    quants = n_ts_qs$quantiles,
    sd_team = map2(
      n_teams, quants,
      ~run_simulations(.x, .y)
    )
  )

  saveRDS(sample_sims, sample_file)
}
```

```{r plot, eval=FALSE, include=FALSE}
sample_sims <- sample_sims %>%
  mutate(
    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
  )

sample_sims %>%
  ggplot(aes(quants, cri, colour = as.factor(n_teams))) +
  geom_line() +
  geom_point(size = 4) +
  geom_hline(yintercept = 1) +
  geom_hline(yintercept = 2, linetype = "dashed") +
  scale_x_continuous(breaks = quantiles) +
  scale_color_brewer(type = "seq", palette = "BuPu") +
  labs(
    title = "95% CrI width depending on teams' true SD and number of teams",
    x = "Teams' true standard deviation",
    y = "95% CrI width",
    colour = "N of teams"
  )
